\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-8pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-3pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

%% ==== Headings ==== 
% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeEducationHeading}[5]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} $\vert$ #2 & #3 \\
      \textit{\small#4} & \textit{\small #5} \\
    \end{tabular*}\vspace{0.5pt}
}

\newcommand{\resumeExperienceHeading}[3]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} {#2} & \textit{#3} \\
    \end{tabular*}\vspace{-3pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}}
      \textbf{#1} $\vert$ \textit{#2} 
    \end{tabular*}\vspace{-3pt}
}

%% ==== Subheadings ====
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[noitemsep]\vspace{-4pt}}
\newcommand{\resumeItemListEnd}{\end{itemize}}


%-------------------------------------------
%%%%%%  Resume STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{center}
  \textbf{\huge Brian Pak} \\
  \vspace*{0.1cm}
  {bpak7@gatech.edu}  $\cdot$ {github.com/brianpak2402} $\cdot$ {linkedin.com/in/brianpakk}  $\cdot$ Atlanta, GA
\end{center}

%-----------EDUCATION-----------------
\section{Education}
    \resumeEducationHeading
      {Georgia Institute of Technology}{Atlanta, GA}{Expected Graduation: May 2024}
      {B.S -- Computer Science, Concentrations: Intelligence \& Media}{GPA: 3.12\vspace{0.1cm}} 
    \textbf{Coursework}{: Data Structures \& Algorithms (Java \& C++), Object-Oriented Programming, Computer Organization, Systems Programming, Automata \& Complexity Theory, Combinatorics, Discrete Mathematics} \\

%--------------EXPERIENCE---------------
\section{Experience}
  \resumeExperienceHeading{GT WebDev}{$\vert$ Software Developer}{August 2022 - Current}
    \resumeItemListStart
      \item {Collaborated with a team to Agile development process to develop a game-based learning platform that guides users in exploring new music.}
      \item {Designed and implemented user authorization on Spotify API with PKCE extension, allowing client secrets to be secured while communicating information with Spotify servers.}
      \item {Maintained real-time data of `upvotes' and `downvotes' of certain songs/albums using WebSockets API, supporting `multiplayer' functionality.}
    \resumeItemListEnd
  
  \resumeExperienceHeading{Freelance Personal Tutor}{}{August 2021 - May 2022}
    \resumeItemListStart
      \item {Prepared personalized lessons in programming fundamentals and object-oriented programming to aid 6 economically-disadvantaged high school students in preparing for advanced standing exams.}
      \item {Composed guides with Notion to assist 3 students at the University of Georgia in studying Automata Theory and Data Structures, helping raise their academic performance by an average of 6\%.}
    \resumeItemListEnd

%-----------PROJECT EXPERIENCE-----------------
\section{Projects}
    \resumeProjectHeading{Unix Utilities}{C}
      \resumeItemListStart
        \item {Implemented a collection of 8 Linux/UNIX command-line commands, including head, tail, env, and wc.}
        \item {Employed C Standard Library Functions to make system calls to the Linux Kernel, allowing the implementation work directly with the device's operating system.}
      \resumeItemListEnd

    \resumeProjectHeading{Stranger Things Showdown!}{C}
      \resumeItemListStart
        \item {Programmed a Stranger Things-themed rock, paper, scissors video game for the GameBoy Advance.}
        \item {Encoded graphics for 7 Stranger Things characters and background scenery into the game by manipulating Direct Memory Access functions and implemented game logic using C programming.}
      \resumeItemListEnd

    \resumeProjectHeading{Geography Quiz}{JavaFX, JUnit, Maven}
      \resumeItemListStart
        \item {Developed a GUI for an interactive geography quiz, which asks players to pair countries with their corresponding continents.}
        \item {Built the frontend of the interface with JavaFX and organized the project through Apache Maven.}
      \resumeItemListEnd

%-----------LEADERSHIP----------------------
\section{Extracurriculars}
  \resumeExperienceHeading{The Agnecy}{}{January 2022 - May 2022}
    \resumeItemListStart
      \item {Implemented a deep neural network of three layers in Python that interprets over 10,000 handwritten
      digits MNIST data to understand fundamental deep learning concepts and basics to ML Libraries.}
      \item {Attended lecture meetings to gain awareness about other AI subfields of interest, like Reinforcement
      Learning, Machine Learning Theory, and Computer Vision.}
    \resumeItemListEnd
  
%-----------SKILLS----------------------
\section{Skills}
    \textbf{Languages}{: Java, C, C++, JavaScript, HTML/CSS, Python} \\
    \textbf{Technologies}{: Git, React.js, styled-components} \\


\end{document}